Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Change resistance

% In the beginning of the transformation the organization has realized the need
% to change and is going towards the initial push.
In many cases the initiative to change came from management, but when presented
wrong the initiative becomes a mandate. Spayd summarizes this as:
``Organizations do not change merely because the boss says so, at least not in
the way that is intended'' [P49]. In that organization the introduction of CMM
was carried out consistently by a mandate, but the collaborative nature of agile
did not comply with such a mindset. A top down mandate may also dilute the
understanding of the reasons for starting the transformation, and further for
agile development overall [P2].

Organizations had bad experiences with prescribing how to carry out Scrum
practices. For instance, doing agile based on checklists would not work [P41].
Benefield described that it was challenging to find a balance between
independence for teams to choose their way and diluting the value and structure
of Scrum [P6]. Giving room for team autonomy is one of the critical facets of
agile, but it must be ensured that teams do not discard practices that add value
and structure.

@@

@@

@@

On a team level numoerous reasons for change resistance were given. For
instance, Fecarotta described the organization of Boeing as risk-averse and
cautious which slows down any change [P14]. The organization was also described
having a deeply rooted status-quo because of high employee retention, which
further hindered change. In some cases it was reported that people worried about
new roles and responsibilities that agile would possibly bring [P44]. For
instance, testers were worried that they would need to take on cross functional
tasks, which would be outside their area of expertise [P18]. Yet another reason
for change resistance was the move from own offices to team areas [P22]. People
were also feeling being monitored because of the increased level of interaction
within the team and between project stakeholders [P45].
One study reported the cultural change required by middle management as the
biggest cause of resistance [P2].

Change resistance was mitigated for instance by education [P45], and one-to-one
discussions [P22]. Change resistance was also softened by using first only teams
willing to try agile, so that insights could be gathered to ease the continued
transformation [P45].

@@

>>>>

% In the beginning of the transformation the organization has realized the need
% to change and is going towards the initial push.
In many cases the initiative to change came from management, but when presented
wrong the initiative becomes a mandate. Spayd summarizes this as:
``Organizations do not change merely because the boss says so, at least not in
the way that is intended'' [P49]. In that organization the introduction of CMM
was carried out consistently by a mandate, but the collaborative nature of agile
did not comply with such a mindset. A top down mandate may also dilute the
understanding of the reasons for starting the transformation, and the
understanding of agile development overall [P2]. O'Connor describes how team
members became sceptical towards agile when implementing mandaetd changes did
not bring any visible benefits [P37].

Organizations had also bad experiences if the implementation of the agile model
was prescribed. For instance, doing Scrum based on checklists of practices would
not work [P41]. Benefield described that it was challenging to find a balance
between independence for teams to choose their way and diluting the value and
structure of Scrum [P6]. Giving room for team autonomy is one of the critical
facets of agile, but it must be ensured that teams do not discard practices that
add value and structure.

@@

% Agile zealots

@@

% People do not speak their minds

@@

On a team level numoerous reasons for change resistance were given. For
instance, Fecarotta described the organization of Boeing as risk-averse and
cautious which slows down any change [P14]. The organization was also described
having a deeply rooted status-quo because of high employee retention, which
further hindered change. In some cases it was reported that people worried about
new roles and responsibilities that agile would possibly bring [P44]. For
instance, testers were worried that they would need to take on cross functional
tasks, which would be outside their area of expertise [P18]. Yet another reason
for change resistance was the move from own offices to team areas [P22]. People
were also feeling being monitored because of the increased level of interaction
within the team and between project stakeholders [P45]. One study reported the
cultural change required for middle management as the biggest cause of
resistance [P2].

In these cases change resistance was mitigated for instance by education [P45],
and one-to-one discussions [P22]. Change resistance was also softened by using
first only teams willing to try agile, so that insights could be gathered to
ease the continued transformation [P45].

Another common form of change resistance that was reported was skepticism.
Seffernick describes how management did on one hand acknowledge benefits of
agile, but on the other explained away the possibilitiy to apply it due to
contract reasons, the current matrix organization, and other organizational
practices [P46]. In that case the director of development still pushed the agile
transformation forward. Skepticism was often created by other similar
misconceptions, including that agile does not work for complex products [P5,
P36], agile needs to be implemented in a prescriptive by-the-book way [P9], that
frequent meetings will cause overhead [P18], and that agile equals avoiding
governance and working without a plan [P8].

@@

% * No value seen by some groups, e.g. mainframe or maintenance [P49]
